---
title: "Pre-Processing BAM Data"
author: "Date created: March 13, 2017"
date: "Last updated on: March 14, 2017"
output: html_document
---

## File adapated from psolymos' [dataprocessing.R script](https://github.com/psolymos/bamanalytics/blob/master/R/dataprocessing.R)

### Preliminaries

#### Define folder and file names for use later

* rootfolder: directory from which you'll pull data and write results
* ssdat: filename (with path extension) of csv with SS information
* intdat: filename (with path and extension) of csv where SS were intersected with environmental correlates 

``` {r setup, echo=F, message=F, warning=F}
require(knitr)
rootfolder <- '../COFI.MBMatrix'
ssdat <- 
indat <- "data/Intersections/BBS_BAM_Atlas_MigLayer_Jan22_2017-zSpGroup.csv"
opts_knit$set(root.dir = rootfolder)
```

#### Load required packages
``` {r}
library(mefa4)
library(RODBC)
library(maptools)
library(QPAD) # not available from CRAN. If want to use it, must get from Peter. 
```

### Load Data Tables

#### SS (site location) Table

* SS
* SSID (unique id based on coordinates, created elsewhere by Nicole)
* Time Zone
* BCR
* Jurisdiction
* XY

``` {r}
tmp <- read.csv(indat, header=T)

```
