---
title: "Pre-Processing BAM Data"
author: "Date created: March 13, 2017"
date: "Last updated on: March 14, 2017"
output: html_document
---

## File adapated from psolymos' [dataprocessing.R script](https://github.com/psolymos/bamanalytics/blob/master/R/dataprocessing.R)

### Preliminaries

#### Define folder and file names for use later

* rootfolder: directory from which you'll pull data and write results
* ssdat: filename (with path and extension) of csv with SS information
* cofipts: filename (with path and extension) of csv where SS were intersected with the BC VRI-based shapefile of forest attributes (for nicole's migratory bird matrix work)
* **Other intersection files can be added here**

``` {r setup, echo=F, message=F, warning=F}
require(knitr)
rootfolder <- '../COFI.MBMatrix'
opts_knit$set(root.dir = rootfolder)

``` {r set.filenames, echo=T}
ssdat <- 
cofipts <- "data/Intersections/BBS_BAM_Atlas_MigLayer_Jan22_2017-zSpGroup-stnID.csv"
lccpts <- 

```

#### Load required packages
``` {r}
library(mefa4)
library(RODBC)
library(maptools)
library(QPAD) # not available from CRAN. If want to use it, must get from Peter. 
```

### Load Data Tables

#### Base SS (site location) Table

* SS
* SSID (unique id based on coordinates, created elsewhere by Nicole)
* Time Zone
* BCR
* Jurisdiction
* XY

``` {r}


```

#### Covariate intersection tables

Moving forward... I think all pre-processing of each table (reclassing, etc) should be done done elsewhere. Or possibly in a script that is sourced below. 

Each chunk below corresponds to a table. If you want to load a specific covariate, switch eval=F to eval=T. Otherwise leave it as is. 

I (Nicole) only have one intersection table for now. 

##### COFI (N.Barker migratory bird matrix collab)
``` {r load.cofi.table}
tmp <- read.csv(cofipts, header=T)
```


##### Land Cover of Canada 2005

``` {r load.lcc, eval=F}

```

##### North American Land Cover

``` {r load.nalc, eval=F}

```
